Sailing the High Seas: A Christian Exploration of Piracy

### 2024-04-29 paper.tex
add Christian connection to free access
add sources to unsubstantiated section

Take the restricted access to academic journal articles, for instance. Many academic
journals require all readers to pay not an insignificant sum to access research articles
that could contain insight that is valuable to the human race as a whole. Because of the
high cost of entry, certain groups are automatically excluded from reading and building
upon the research that has already been done. \citeauthor{barlow:wine} puts the situation
eloquently in \citetitle{barlow:wine} when he says, \textcquote{barlow:wine}[.]{%
  I am not comfortable with a model which will restrict inquiry to the wealthy%
}
In the case of academic journal articles, why shouldn't anyone be able to better
themselves by consuming quality research articles? All humans should be allowed
to continue to learn more about God's creation without being bound by their
financial status. Just as how someone can go to the library and checkout any
book that tickles their fancy, they should be freely able to learn from the
ongoing research of our world. Of course one should recognize that not all
information is safe or helpful to be freely available on the internet, but that
is a topic for a later section.

@@

Medical journals are not the only source of information that can sit behind a paywall.
Sometimes, as in the previous case, there is information that one might argue is unjustly
kept away from the common man. What one considers to be unjust is subjective, but the idea
is that piracy is a tool that consumers can employ to fight systems that they deem to be
unjust. Without piracy, one might have to roll over and accept their limited access or
resort to a more extreme and likely illegal approach. To put it another way, piracy acts
as a check on businesses to discourage them from integrating unpopular, anti-consumer
practices into their business model. When a consumer wants to purchase something and they
cannot afford it, they might start to look for alternative way of obtaining it. But, when
they can afford it and they think it is fairly priced, they will purchase it. Thus, piracy
is often where tech-savvy persons turn to when they need something that they feel is
exorbitantly priced, but is not often utilized when they feel the purchase is worthwhile.
This way, piracy acts as a safeguard for consumers when they feel they are being taken
advantage of by predatory business practices.
% XXX the statements in the paragraph above are largely unsubstantiated >:D
% XXX add darnton:pirating-and-publishing and bohannon:everyone sources if needed

>>>>

Take the restricted access to academic journal articles, for instance. Many academic
journals require all readers to pay not an insignificant sum to access research articles
that could contain insight that is valuable to the human race as a whole. Because of the
high cost of entry, certain groups are automatically excluded from reading and building
upon the research that has already been done. \citeauthor{barlow:wine} puts the situation
eloquently in \citetitle{barlow:wine} when he says, \textcquote{barlow:wine}[.]{%
  I am not comfortable with a model which will restrict inquiry to the wealthy%
}
In the case of academic journal articles, why shouldn't anyone be able to better
themselves by consuming quality research articles? All humans should be allowed to
continue to learn more about God's creation without being bound by their financial status.
The Bible encourages one to pursue knowledge. Proverbs 1:5 reads, \textquote{\textins{l}et
the wise hear and increase in learning, and the one who understands obtain guidance.}
One's ability to live out this verse should not be artificially hindered by financial
station. Just as how someone can go to the library and checkout any book that tickles
their fancy, they should be freely able to learn from the ongoing research of our world.
Of course one should recognize that not all information is safe or helpful to be freely
available on the internet, but that is a topic for a later section.

@@

Medical journals are not the only source of information that can sit behind a paywall.
Sometimes, as in the previous case, there is information that one might argue is unjustly
kept away from the common man. What one considers to be unjust is subjective, but the idea
is that piracy is a tool that consumers can employ to fight systems that they deem to be
unjust. Without piracy, one might have to roll over and accept their limited access or
resort to a more extreme and likely illegal approach. To put it another way, piracy acts
as a check on businesses to discourage them from integrating unpopular, anti-consumer
practices into their business model. When a consumer wants to purchase something and they
cannot afford it, they might start to look for alternative way of obtaining it. But, when
they can afford it and they think it is fairly priced, they will purchase it.

According to a survey conducted by MUSO, \textcquote{muso-about}{a data company that
provides the most complete and trusted view of global piracy and unlicensed media
consumption,} the most common reasons that users pirate is \textcquote{vice-pirates}{the
content they were looking for wasn’t legally available (34 percent) was too cumbersome or
difficult to access (34 percent), or wasn’t affordable (35 percent).} The reason most
people pirate is not that they are not willing to pay for the content, but that they
cannot legally obtain it any other way, that it was too hard to access, or that it was not
affordable. In the latter two cases, one can see the consumer's power to protest poorly
designed systems or unaffordable prices. Thus, piracy is often where tech-savvy persons
turn to when they need something that they feel is exorbitantly priced, but is not often
utilized when they feel the purchase is worthwhile. This way, piracy acts as a safeguard
for consumers when they feel they are being taken advantage of by predatory business
practices.
